R for Clinical Study Reports and Submission

### 2021-12-10 tlf-efficacy-km.Rmd
reformat the code

```{r}
adtte_ttde <- adtte %>%
  filter(PARAMCD == "TTDE") %>%
  select(TRTP, TRTAN, AVAL, CNSR) %>%
  mutate(TRTP = forcats::fct_reorder(TRTP, TRTAN), # Recorder levels
         AVAL_m = AVAL/30.4367) # convert Day to Month
```

@@

```{r}
risk_tab <- function(tlim, time) {
  n_risk <- NULL
  for (i in tlim){
    n_risk <- c(n_risk, sum(time >= i))
  }
  return(n_risk)
}
```

@@

```{r}
# Save as a PNG file
png(file = "tlf/fig_km1.png", width = 3000, height = 2000, res = 400)

par(mfrow = c(1, 1), mar = c(9, 11, 1, 1), family = "Times") # Set plot margins

plot(fit, xlab = "Time in Months", ylab = "Survival probability", lwd = 2, mark.time = T, col = c(2, 3, 4), lty = c(1, 2, 3))
legend("topright", lwd = 2, cex = 0.9, col = c(2, 3, 4), lty = c(1, 2, 3), legend = levels(adtte_ttde$TRTP), bty = "n")
mtext("Number at risk", side = 1, line = 4, at = 0)
grid <- 0:6
mtext(c("Placebo", risk_tab(grid,adtte_ttde$AVAL[adtte_ttde$TRTP=="Placebo"]/30.4367)), side = 1, adj = c(1, rep(NA, length(grid))), line = 5, at = c(-0.8, grid))
mtext(c("Xanomeline Low Dose", risk_tab(grid,adtte_ttde$AVAL[adtte_ttde$TRTP=="Xanomeline Low Dose"]/30.4367)), side = 1, adj = c(1, rep(NA, length(grid))), line = 6, at = c(-0.8, grid))
mtext(c("Xanomeline High Dose", risk_tab(grid,adtte_ttde$AVAL[adtte_ttde$TRTP=="Xanomeline High Dose"]/30.4367)), side = 1, adj = c(1, rep(NA, length(grid))), line = 7, at = c(-0.8, grid))

@@

```{r}
# Create RTF figure
rtf_read_png("tlf/fig_km1.png") %>% # Read the PNG file from the file path
  rtf_title("Kaplan-Meier Plot for Time to First Dermatologic Event by Treatment Group", "All Participants") %>% # Add title or subtitle
  rtf_footnote("footnote") %>% # Add footnote
  rtf_source("[datasource: adam-adtte]") %>% # Add data source
  rtf_figure(fig_width = 6, fig_height = 4) %>% # Set proportional figure size to the original PNG figure size
  rtf_encode(doc_type = "figure") %>% # Encode rtf as figure
  write_rtf(file = "tlf/fig_km1.rtf")
```

@@

```{r}
# Save as PNG file
grid.draw.ggsurvplot <- function(x) survminer:::print.ggsurvplot(x, newpage = FALSE)
ggsave("tlf/fig_km2.png", plot = fig_km2, width = 10, height = 6)

# Create RTF figure
rtf_read_png("tlf/fig_km2.png") %>% # Read PNG files from the file path
  rtf_title("Kaplan-Meier Plot for Time to First Dermatologic Event by Treatment Group", "All Participants") %>% # Add title or subtitle
  rtf_footnote("footnote") %>% # Add footnote
  rtf_source("[datasource: adam-adtte]") %>% # Add data source
  rtf_figure(fig_width = 6, fig_height = 3.6) %>% # Set proportional figure size to the original PNG figure size
  rtf_encode(doc_type = "figure") %>% # Encode rtf as figure
  write_rtf(file = "tlf/fig_km2.rtf")
```

@@

```{r}
# Estimate KM
surv_mod <- visR::estimate_KM(data = adtte_ttde, strata = "TRTP", AVAL = "AVAL_m")
# save plot
ggplot2::theme_set(theme_bw() + theme(text = element_text(family = 'serif')))

png("tlf/fig_km3.png", width = 3000, height = 2000, res = 400)
KM <- visR::visr(surv_mod,
           y_label = "Survival Probability\n",
           x_label = "Time in Months",
           x_ticks = 0:6,
           y_ticks = seq(0,1,0.1),
           legend_position = "bottom") %>%
    add_CNSR()

@@

```{r}
# Create RTF figure
rtf_read_png("tlf/fig_km3.png") %>% # Read the PNG file from the file path
  rtf_title("Kaplan-Meier Plot for Time to First Dermatologic Event by Treatment Group", "All Participants") %>% # Add title or subtitle
  rtf_footnote("footnote") %>% # Add footnote
  rtf_source("[datasource: adam-adtte]") %>% # Add data source
  rtf_figure(fig_width = 6, fig_height = 4) %>% # Set proportional figure size to the original PNG figure size
  rtf_encode(doc_type = "figure") %>% # Encode rtf as figure
  write_rtf(file = "tlf/fig_km3.rtf")
```

@@

```{r}
# save plot as PDF file
pdf.options(reset = TRUE, onefile = FALSE)
pdf("tlf/fig_km3.pdf", width = 12, height = 6)
KM <- visR::visr(surv_mod,
           y_label = "Survival Probability\n",
           x_label = "Time in Months",
           x_ticks = 0:6,
           y_ticks = seq(0,1,0.1)) %>%
    add_CNSR()

@@

title <- cowplot::ggdraw() + 
  cowplot::draw_label(
    "Kaplan-Meier Plot for Time to First Dermatologic Event by Treatment Group\nAll Participants",
    fontfamily = "serif",
    size=12
  ) 
caption <- cowplot::ggdraw() + 
  cowplot::draw_label(
    paste0("\nProgram: tlf-efficacy-km.Rmd [", Sys.time(), "]\n[Datasource: adam-adtte]"),
    fontfamily = "serif",
    size=12
  )

KM2 <- cowplot::plot_grid(
  title, KM1, caption,
  ncol = 1,
  rel_heights = c(0.1,0.8,0.1)
) #%>%
 # visR::apply_theme(theme_times)
print(KM2)
dev.off()
```

>>>>

```{r}
adtte_ttde <- adtte %>%
  filter(PARAMCD == "TTDE") %>%
  select(TRTP, TRTAN, AVAL, CNSR) %>%
  mutate(TRTP = forcats::fct_reorder(TRTP, TRTAN), # Recorder levels
         AVAL_m = AVAL / 30.4367) # convert Day to Month
```

@@

```{r}
risk_tab <- function(tlim, time) {
  n_risk <- NULL
  for (i in tlim) {
    n_risk <- c(n_risk, sum(time >= i))
  }
  return(n_risk)
}
```

@@

```{r}
# Save as a PNG file
png(
  file = "tlf/fig_km1.png",
  width = 3000,
  height = 2000,
  res = 400
)

par(mfrow = c(1, 1),
    mar = c(9, 11, 1, 1),
    family = "Times") # Set plot margins and font style

plot(
  fit,
  xlab = "Time in Months",
  ylab = "Survival probability",
  lwd = 2,
  mark.time = T,
  col = c(2, 3, 4),
  lty = c(1, 2, 3)
)
legend(
  "topright",
  lwd = 2,
  cex = 0.9,
  col = c(2, 3, 4),
  lty = c(1, 2, 3),
  legend = levels(adtte_ttde$TRTP),
  bty = "n"
)
mtext("Number at risk",
      side = 1,
      line = 4,
      at = 0)
grid <- 0:6
mtext(
  c("Placebo", risk_tab(grid, adtte_ttde$AVAL_m[adtte_ttde$TRTP == "Placebo"])),
  side = 1,
  adj = c(1, rep(NA, length(grid))),
  line = 5,
  at = c(-0.8, grid)
)
mtext(
  c("Xanomeline Low Dose",
    risk_tab(grid, adtte_ttde$AVAL_m[adtte_ttde$TRTP == "Xanomeline Low Dose"])),
  side = 1,
  adj = c(1, rep(NA, length(grid))),
  line = 6,
  at = c(-0.8, grid)
)
mtext(
  c("Xanomeline High Dose",
    risk_tab(grid, adtte_ttde$AVAL_m[adtte_ttde$TRTP == "Xanomeline High Dose"])),
  side = 1,
  adj = c(1, rep(NA, length(grid))),
  line = 7,
  at = c(-0.8, grid)
)

@@

```{r}
# Create RTF figure
rtf_read_png("tlf/fig_km1.png") %>% # Read the PNG file from the file path
  rtf_title(
    "Kaplan-Meier Plot for Time to First Dermatologic Event by Treatment Group",
    "All Participants"
  ) %>% # Add title or subtitle
  rtf_footnote("footnote") %>% # Add footnote
  rtf_source("[datasource: adam-adtte]") %>% # Add data source
  rtf_figure(fig_width = 6, fig_height = 4) %>% # Set proportional figure size to the original PNG figure size
  rtf_encode(doc_type = "figure") %>% # Encode rtf as figure
  write_rtf(file = "tlf/fig_km1.rtf")
```

@@

```{r}
# Save as PNG file
# grid.draw.ggsurvplot <- function(x) survminer:::print.ggsurvplot(x, newpage = FALSE)
ggsave("tlf/fig_km2.png",
       plot = fig_km2,
       width = 10,
       height = 6)

# Create RTF figure
rtf_read_png("tlf/fig_km2.png") %>% # Read PNG files from the file path
  rtf_title(
    "Kaplan-Meier Plot for Time to First Dermatologic Event by Treatment Group",
    "All Participants"
  ) %>% # Add title or subtitle
  rtf_footnote("footnote") %>% # Add footnote
  rtf_source("[datasource: adam-adtte]") %>% # Add data source
  rtf_figure(fig_width = 6, fig_height = 3.6) %>% # Set proportional figure size to the original PNG figure size
  rtf_encode(doc_type = "figure") %>% # Encode rtf as figure
  write_rtf(file = "tlf/fig_km2.rtf")
```

@@

```{r}
# Estimate KM data point
surv_mod <-
  visR::estimate_KM(data = adtte_ttde,
                    strata = "TRTP",
                    AVAL = "AVAL_m")
# save plot with white background and Times New Roman font
ggplot2::theme_set(theme_bw() + theme(text = element_text(family = 'serif')))

png("tlf/fig_km3.png",
    width = 3000,
    height = 2000,
    res = 400)
KM <- visR::visr(
  surv_mod,
  y_label = "Survival Probability\n",
  x_label = "Time in Months",
  x_ticks = 0:6,
  y_ticks = seq(0, 1, 0.1),
  legend_position = "bottom"
) %>%
  add_CNSR()

@@

```{r}
# Create RTF figure
rtf_read_png("tlf/fig_km3.png") %>% # Read the PNG file from the file path
  rtf_title(
    "Kaplan-Meier Plot for Time to First Dermatologic Event by Treatment Group",
    "All Participants"
  ) %>% # Add title or subtitle
  rtf_footnote("footnote") %>% # Add footnote
  rtf_source("[datasource: adam-adtte]") %>% # Add data source
  rtf_figure(fig_width = 6, fig_height = 4) %>% # Set proportional figure size to the original PNG figure size
  rtf_encode(doc_type = "figure") %>% # Encode rtf as figure
  write_rtf(file = "tlf/fig_km3.rtf")
```

@@

```{r}
# save plot as PDF file
pdf.options(reset = TRUE, onefile = FALSE)
pdf("tlf/fig_km3.pdf", width = 12, height = 6)

KM <- visR::visr(
  surv_mod,
  y_label = "Survival Probability\n",
  x_label = "Time in Months",
  x_ticks = 0:6,
  y_ticks = seq(0, 1, 0.1)
) %>%
  add_CNSR()

@@

title <- cowplot::ggdraw() +
  cowplot::draw_label(
    "Kaplan-Meier Plot for Time to First Dermatologic Event by Treatment Group\nAll Participants",
    fontfamily = "serif",
    size = 12
  )
caption <- cowplot::ggdraw() +
  cowplot::draw_label(
    paste0(
      "\nProgram: tlf-efficacy-km.Rmd [",
      Sys.time(),
      "]\n[Datasource: adam-adtte]"
    ),
    fontfamily = "serif",
    size = 12
  )

KM2 <- cowplot::plot_grid(title,
                          KM1,
                          caption,
                          ncol = 1,
                          rel_heights = c(0.1, 0.8, 0.1)) #%>%
# visR::apply_theme(theme_times)
print(KM2)
